On change of priors in one-vs-one classification methods

### 2025-05-08 coupling.tex
Fix proposition 2

There are many Bayes covariant methods. In this section we will show that 
\begin{itemize} 
	\item arboreal coupling methods are Bayes covariant,
	\item Bayes covariant methods can be ensembled,
	\item describe all Bayes covariant methods for $K=3$.
\end{itemize}

We start by defining the property $BC_{ij}$ (the notation stands for \emph{Bayes covariant when restricted to classes} $i$ and $j$) of a coupling method. A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal.

@@

\begin{itemize}
	\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$,
	\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant,
	\item[c)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant,
	\item[d)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Proposition \ref{lem:transitivity}).
\end{itemize}

@@

An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$. It follows using from b) and d) that the method is Bayes covariant.

>>>>

There are many Bayes covariant methods. The simplest example are arboreal coupling methods. They are not canonical, but with the help of ensembling, one can construct also canonical coupling methods.

A very helpful aid to study Bayes covariant methods is property $BC_{ij}$ (the notation stands for \emph{Bayes covariant when restricted to classes} $i$ and $j$). A coupling method $\boldsymbol{v}$ satisfies $BC_{ij}$ if for any change of priors $\pi$ and any  pairwise data $\boldsymbol{R}$ the odds of classes $C_i$ to $C_j$ predicted by $\boldsymbol{v}(\boldsymbol{R}^\pi)$ and $\bigl(\boldsymbol{v}(\boldsymbol{R})\bigr)^\pi$ are equal. Using  notation for odds from Section \ref{sec:one-vs-one}, one has
\begin{align}
	\alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R}^\pi) \bigr) = \alpha_{ij} \bigl(\boldsymbol{v}(\boldsymbol{R})^\pi \bigr)
\end{align}

@@

\begin{itemize}
	\item[a)] a Bayes covariant coupling method satisfies $BC_{ij}$ for any $i\not= j$ (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
	%\item[b)] if a coupling method satisfies $BC_{12}, BC_{23}, \ldots, BC_{(K-1),K}$ then it is Bayes covariant (see Proposition \ref{prop:bcprop}),
	\item[b)] if a coupling method satisfies $BC_{ij}$ for all $i\not= j$ then it is Bayes covariant (see Proposition \ref{prop:bcprop} in Appendix \ref{app:bc1}),
	\item[c)] if a coupling method satisfies $BC_{ij}$ and $BC_{jk}$ then it satisfies $BC_{ik}$ (see Lemma \ref{lem:transitivity}).
\end{itemize}

@@

An arboreal coupling method $\boldsymbol{t}$ induced by a spanning tree $T$ on the classes satisfies $BC_{ij}$ whenever the edge $C_iC_j$ belongs to $T$. Since any pair of vertices is connected by a path, it follows from transitivity of $BC_{ij}$ (property c) that the assumption of b) holds and thus the coupling method is Bayes covariant.

### 2025-05-08 theory.tex
Fix proposition 2

\subsection{One-vs-on classification}

@@

Let us outline what kind of conditions may be desirable in a coupling method. In %Section \ref{sec:des:exact} 
this section
 we will describe exact mathematical criteria, while in section \ref{sec:des:inexact} we shall describe more flexible properties.

>>>>

\subsection{One-vs-one classification} \label{sec:one-vs-one}

@@

%Let us outline what kind of exact conditions may be desirable in a coupling method. 
In %Section \ref{sec:des:exact} 
this section
 we will describe exact mathematical criteria that one may impose on a coupling method, while in section \ref{sec:des:inexact} we shall describe more flexible properties.
